### 2013-09-22 exact_learning/paper.tex
use past tense when discussing literature.

Recently, there has been an increase in research in learning structured
prediction models where standard exact inference techniques are not applicable,
in particular in the computer vision community.
The influence of approximate inference on structural support vector machine
learning was first analyzed by  \citet{finley2008training}.
\citet{finley2008training} show convergence results for under-generating and
over-generating inference procedures, meaning methods that find suboptimal, but
feasible solutions, and optimal solutions from a larger (unfeasible) set,
respectively.
\citet{finley2008training} demonstrate that over-generating approaches---in
particular linear programming (LP)---perform best on the considered model.
They also show that learning parameters with the LP relaxation minimizes a
bound on the empirical risk when extending the target domain to the relaxed
solutions.
We argue that extending the target domain in this way is unnatural for many applications,
and aim at optimizing the non-relaxed objective directly, minimizing
the original empirical risk. This is an important difference, as relaxed solutions
are usually not acceptable in practice.

@@

Recently, \citet{meshi2010learning}, \citet{hazan2010primal} and
\citet{komodakis2011efficient} introduced formulations for joint inference and
learning using duality.
In particular, \citet{hazan2010primal} demonstrate the performance of their
model on an image denoising task, where it is possible to learn a large number
of parameters efficiently.
While these approaches show great promise, in particular for pixel-level or
large-scale problems, they perform approximate inference and learning, and do
not relate their results back to the original SSVM objective they approximate.
It is unclear how they compare to standard structured prediction approaches
on real-world applications.

>>>>

Recently, there has been an increase in research in learning structured
prediction models where standard exact inference techniques are not applicable,
in particular in the computer vision community.
The influence of approximate inference on structural support vector machine
learning was first analyzed by \citet{finley2008training}.
\citet{finley2008training} showed convergence results for under-generating and
over-generating inference procedures, meaning methods that find suboptimal, but
feasible solutions, and optimal solutions from a larger (unfeasible) set,
respectively.
\citet{finley2008training} demonstrated that over-generating approaches---in
particular linear programming (LP)---perform best on the considered model.
They also show that learning parameters with the LP relaxation minimizes a
bound on the empirical risk when extending the target domain to the relaxed
solutions.
We argue that extending the target domain in this way is unnatural for many applications,
and aim at optimizing the non-relaxed objective directly, minimizing
the original empirical risk. This is an important difference, as relaxed solutions
are usually not acceptable in practice.

@@

Recently, \citet{meshi2010learning}, \citet{hazan2010primal} and
\citet{komodakis2011efficient} introduced formulations for joint inference and
learning using duality.
In particular, \citet{hazan2010primal} demonstrated the performance of their
model on an image denoising task, where it is possible to learn a large number
of parameters efficiently.
While these approaches show great promise, in particular for pixel-level or
large-scale problems, they perform approximate inference and learning, and do
not relate their results back to the original SSVM objective they approximate.
It is unclear how they compare to standard structured prediction approaches
on real-world applications.

### 2013-09-22 intro.tex
use past tense when discussing literature.

There have been several previous studies on learning structural support vector
machines, and learning for conditional random fields. The impact of approximate
inference was first investigated by \citet{finley2008training}, applying
structural support vector machines to multi-label data. Later, different works
investigated how to combine approximate inference and learning in a single
framework. \citet{meshi2010learning, komodakis2011efficient}, and
\citet{hazan2010primal} approach the problem using duality, and formulate
learning and inference as a joint optimization problem.
\citet{stoyanov2011empirical}, and later \citet{jancsarylearning} and
\citet{krahenbuhlparameter} formulate learning structured prediction as
optimizing a \emph{prediction engine}, that takes into account all aspects of
the model, in particular the inference algorithm used.
In this work, on the other hand, we follow the well-established algorithms for
learning structural support vector machines, and investigate how we can use the
available inference algorithms to obtain good results within a reasonable
time-frame.

\citet{nowozin2010parameter} provide a detailed evaluation of different aspects
of learning object class segmentation, that is somewhat orthogonal to this
work. Their work considers the choice of features, number of superpixels and
pairwise potentials for conditional maximum likelihood learning of
tree-structured CRFs.  \citet{nowozin2010parameter} also compare conditional
maximum likelihood learning with maximum margin learning, finding little
difference in accuracy.
We focus our work on the more popular neighborhood graphs, which do not allow
for efficient inference.  Therefore, conditional maximum likelihood learning is
intractable in our setting. For our studies, we fix the considered feature set,
and vary the maximum margin learning algorithm. Despite this seemingly limited
setup, we can make out large differences in the applicability of some of the
commonly used methods. For comparison, we also evaluate the learning algorithms
on chain CRFs, where efficient inference is possible.
More recently, \citet{lucchi2013learning} propose a novel algorithm for
efficiently learning structured prediction for semantic segmentation, using
approximate inference. In Chapter~\ref{ch:exact_learning}, we develop an
algorithm that runs in similar time to the one proposed by
\citet{lucchi2013learning}, which is able to learn a CRF to the exact optimum on
the same dataset.

>>>>

There have been several previous studies on learning structural support vector
machines, and learning for conditional random fields. The impact of approximate
inference was first investigated by \citet{finley2008training}, applying
structural support vector machines to multi-label data. Later, different works
investigated how to combine approximate inference and learning in a single
framework. \citet{meshi2010learning, komodakis2011efficient}, and
\citet{hazan2010primal} approached the problem using duality, and formulate
learning and inference as a joint optimization problem.
\citet{stoyanov2011empirical}, and later \citet{jancsarylearning} and
\citet{krahenbuhlparameter} formulated learning structured prediction as
optimizing a \emph{prediction engine}, that takes into account all aspects of
the model, in particular the inference algorithm used.
In this work, on the other hand, we follow the well-established algorithms for
learning structural support vector machines, and investigate how we can use the
available inference algorithms to obtain good results within a reasonable
time-frame.

\citet{nowozin2010parameter} provided a detailed evaluation of different aspects
of learning object class segmentation, that is somewhat orthogonal to this
work. Their work considers the choice of features, number of superpixels and
pairwise potentials for conditional maximum likelihood learning of
tree-structured CRFs.  \citet{nowozin2010parameter} also compared conditional
maximum likelihood learning with maximum margin learning, finding little
difference in accuracy.
We focus our work on the more popular neighborhood graphs, which do not allow
for efficient inference.  Therefore, conditional maximum likelihood learning is
intractable in our setting. For our studies, we fix the considered feature set,
and vary the maximum margin learning algorithm. Despite this seemingly limited
setup, we can make out large differences in the applicability of some of the
commonly used methods. For comparison, we also evaluate the learning algorithms
on chain CRFs, where efficient inference is possible.
More recently, \citet{lucchi2013learning} proposed a novel algorithm for
efficiently learning structured prediction for semantic segmentation, using
approximate inference. In Chapter~\ref{ch:exact_learning}, we develop an
algorithm that runs in similar time to the one proposed by
\citet{lucchi2013learning}, which is able to learn a CRF to the exact optimum on
the same dataset.

### 2013-09-22 itm/paper.tex
use past tense when discussing literature.

Later, \citet{banerjee2005clustering} introduced the concept of Bregman
Information, generalizing mutual information of distributions, and showed how
this leads to a natural formulation of several clustering algorithms.
%
\citet{barber2006kernelized} construct a soft clustering by using a parametric model of $p(Y\given X)$.
%
The framework of mutual information based clustering was extended to
non-parametric entropy estimates by \citet{faivishevsky2010nonparametric}.
They use a nearest neighbor based estimator of the mutual information, called
MeanNN, that takes into account all possible neighborhoods, therefore combining
global and local influences. The approximate mutual information is maximized
using local search over labels.
%discuss this later in detail
%While optimizing MeanNN allows for non-convex
%clusters, in practice the result is strongly biased towards compact, convex
%regions. This can be explained by a close connections of MeanNN to $k$-Means,
%see Section~\ref{discussion} for an in-depth discussion.

Clustering algorithms based on minimum spanning trees have been studied early
on in the statistics community, due to their efficiency.  One of the earliest
methods is single-link agglomerative clustering~\citep{gower1969minimum}.
Single-link agglomerative clustering can be understood as a minimum spanning
tree-based approach in which the largest edge is removed until the desired
number of components is reached.  \citet{zahn1971graph} refines this criterion
by cutting edges that are longer than other edges in the vicinity. This
approach requires tuning several constants by hand. More recently,
\citet{grygorash2006minimum} proposed a hierarchical MST-based clustering
approach that iteratively cuts edges, merges points in the resulting
components, and rebuilds the spanning tree.
We limit our discussion to the most widely used algorithm from~\citep{gower1969minimum}.
%
\section[Clustering Using Non-Parametric Entropy Estimates]{Clustering Using\linebreak Non-Parametric Entropy Estimates}
In general, the goal of clustering can be formulated as follows: 
given a finite collection of samples $\mathbf{x} = (x_1, \dotsc, x_n)$, we want to 
assign cluster-memberships $\mathbf{y} = (y_1, \dotsc, y_n ), y_i \in \{1, \dotsc k\}$ to these samples.
%
We adopt the viewpoint of information theoretic clustering of \citet{gokcay2002information}, 
where the $x_i$ are considered i.i.d{.} samples from a distribution $p(X)$, and the 
$y_i$ are found such that the mutual information $I(X, Y)$ between the distribution $p(X)$ and the
assigned labels $p(Y)$ is maximized.
We can rewrite this objective as 
\begin{align}
         I(X, Y)
        &= D_{\text{KL}}(p(X, Y) \parallel p(X) p(Y)) = H(X) - \sum_{y=1}^k p(Y{=}y) H(X \given Y {=} y)
\end{align}
where
\begin{itemize}
    \item $\displaystyle D_\text{KL}(p(X) \parallel q(X))\, = \int_\mathcal{X} p(X) \ln\left(\frac{p(X)}{q(X)}\right)\,dX$ is the Kullback-Leibler divergence,
\item $\displaystyle H(X)\, = \int_\mathcal{X} p(X) \ln(p(X))\,dX$ is the differential entropy, and
\item $\displaystyle H(X \given Y{=}y)\, = \int_\mathcal{X} p(X \given Y {=}y) \ln(p(X \given Y {=} y))\,dX$ is the conditional differential entropy.
    \end{itemize}
Expressing the mutual information in terms of the entropy is convenient, since
the objective then decomposes over the values of $Y$. 
%
Additionally, $H(X)$ is independent of the distribution of $Y$ and therefore
does not influence the search over $\mathbf{y}$.

>>>>

Later, \citet{banerjee2005clustering} introduced the concept of Bregman
Information, generalizing mutual information of distributions, and showed how
this leads to a natural formulation of several clustering algorithms.
%
\citet{barber2006kernelized} constructed a soft clustering by using a parametric model of $p(Y\given X)$.
%
The framework of mutual information based clustering was extended to
non-parametric entropy estimates by \citet{faivishevsky2010nonparametric}.
They use a nearest neighbor based estimator of the mutual information, called
MeanNN, that takes into account all possible neighborhoods, therefore combining
global and local influences. The approximate mutual information is maximized
using local search over labels.
%discuss this later in detail
%While optimizing MeanNN allows for non-convex
%clusters, in practice the result is strongly biased towards compact, convex
%regions. This can be explained by a close connections of MeanNN to $k$-Means,
%see Section~\ref{discussion} for an in-depth discussion.

Clustering algorithms based on minimum spanning trees have been studied early
on in the statistics community, due to their efficiency.  One of the earliest
methods is single-link agglomerative clustering~\citep{gower1969minimum}.
Single-link agglomerative clustering can be understood as a minimum spanning
tree-based approach in which the largest edge is removed until the desired
number of components is reached.  \citet{zahn1971graph} refined this criterion
by cutting edges that are longer than other edges in the vicinity. This
approach requires tuning several constants by hand. More recently,
\citet{grygorash2006minimum} proposed a hierarchical MST-based clustering
approach that iteratively cuts edges, merges points in the resulting
components, and rebuilds the spanning tree.
We limit our discussion to the most widely used algorithm from~\citep{gower1969minimum}.
%
\section[Clustering Using Non-Parametric Entropy Estimates]{Clustering Using\linebreak Non-Parametric Entropy Estimates}
In general, the goal of clustering can be formulated as follows: 
given a finite collection of samples $\mathbf{x} = (x_1, \dotsc, x_n)$, we want to 
assign cluster-memberships $\mathbf{y} = (y_1, \dotsc, y_n ), y_i \in \{1, \dotsc k\}$ to these samples.
%
We adopt the viewpoint of information theoretic clustering of \citet{gokcay2002information}, 
where the $x_i$ are considered i.i.d{.} samples from a distribution $p(X)$, and the 
$y_i$ are found such that the mutual information $I(X, Y)$ between the distribution $p(X)$ and the
assigned labels $p(Y)$ is maximized.
We can rewrite this objective as 
\begin{align}
         I(X, Y)
        &= D_{\text{KL}}(p(X, Y) \parallel p(X) p(Y)) = H(X) - \sum_{y=1}^k p(Y{=}y) H(X \given Y {=} y)
\end{align}
where
\begin{itemize}
    \item $\displaystyle D_\text{KL}(p(X) \parallel q(X))\, = \int_\mathcal{X} p(X) \ln\left(\frac{p(X)}{q(X)}\right)\,dX$ is the Kullback-Leibler divergence,
\item $\displaystyle H(X)\, = \int_\mathcal{X} p(X) \ln(p(X))\,dX$ is the differential entropy, and
\item $\displaystyle H(X \given Y{=}y)\, = \int_\mathcal{X} p(X \given Y {=}y) \ln(p(X \given Y {=} y))\,dX$ is the conditional differential entropy.
    \end{itemize}
Expressing the mutual information in terms of the entropy is convenient, since
the objective then decomposes over the values of $Y$. 
%
Additionally, $H(X)$ is independent of the distribution of $Y$ and therefore
does not influence the search over $\mathbf{y}$.

### 2013-09-22 main.tex
fix some equation numbering.
corrections luisa
visualizations for experiment datasets.
use past tense when discussing literature.

\documentclass[12pt,toc=bibnumbered, a4paper,twoside,DIV=11,BCOR=.5cm]{scrbook}
%\documentclass[12pt,toc=bibnumbered, a4paper,twoside,DIV=calc]{scrbook}
%\documentclass[12pt,toc=bibnumbered, a4paper,twoside]{book}

\usepackage[colorlinks=True, citecolor=blue!50!black, linkcolor=red!50!black, urlcolor=blue!70!black]{hyperref}
\usepackage{refstyle}
\usepackage{amssymb}
\usepackage{amstext}
\usepackage{amsmath}
\usepackage{microtype}
\usepackage{natbib}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{tabu}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{mdwlist}
\usepackage[noend]{algpseudocode}
\usepackage[small]{caption}
\usepackage{setspace}
\usepackage{color}
\usepackage{minted}
\usepackage[german,english]{babel}
%\renewcommand*\sfdefault{avant}
\usepackage{helvet}
%\usepackage[defaultsans]{droidsans}
%\renewcommand*\sfdefault{lmssq}

@@

@@

\newcommand{\given}{\, | \,}
\newcommand{\B}[1]{\textbf{#1}}

@@

\section{Future Directions}
There are several directions for future research that we think would be
interesting to pursue as an extension of the presented results:
\paragraph{Large-Scale Weakly Supervised Object Class Segmentation}
We demonstrated a new method for object class segmentation using only weak
supervision. One of the main advantages of such a method is that it is
potentially able to exploit the large amount of weakly labeled data that
is available on the internet. Using additional, weakly labeled training data,
and evaluating on the given, manually annotated data, is therefore a promising
path for improving the presented results.
\paragraph{Inference Machines}
Recently \citet{stoyanov2011empirical} started a new trend in structured
prediction, which is sometimes called ``inference machines''. The basic
principle is simple: the process of prediction \emph{using a given inference
procedure} is viewed as a feed-forward method for prediction, and parameters of this
prediction process are optimized directly using empirical risk minimization. The work of
\citet{stoyanov2011empirical}, used loopy belief propagation as their inference
algorithm and the optimization is carried out simply using gradient descent on
the non-convex but differentiable loss function.  Other recent work in this
direction includes \citet{krahenbuhlparameter}, who used mean-field inference
in a fully connected conditional random field and \citet{jancsarylearning}, who
used closed form inference in a Gaussian CRF\@.
While these algorithms show great promise, their relation to the traditional
approach of structured prediction used in this work is mostly unclear. In particular,
if exact traditional learning is possible in a model, it is uncertain how much
in accuracy and efficiency can be gained by direct empirical risk minimization.
Only limited empirical comparison is available, and we are not aware of theoretical
work in this direction, leaving much room for future investigation.
\paragraph{Non-Linear Models}
In this work, we only considered models that are linear in the input features---though
features are highly non-linear in the original input pixels. Allowing non-linear
interactions increases the representational power of a CRF, possibly leading
to more accurate prediction results.
Kernelization of structural support vector machines is straight-forward in theory, but
had only limited success in the context of CRFs for image
segmentation~\citep{lucchi2012structured}.
Two major alternatives for non-linear CRFs were proposed in the literature,
conditional neural fields~\citep{peng2009conditional} based on neural networks,
and decision tree fields~\citep{nowozin2011decision}, based on decision trees.
Conditional neural fields have only been applied to sequence classification so far,
and extending them to our setting of semantic image segmentation would be very
interesting. Decision tree fields~(DTFs) on the other hand have been applied to loopy
graphs for image processing, but not for higher-level tasks such as semantic
segmentation. If it is possible to include context in a meaningful way, it
might be possible to address even object-centric tasks such as object class
segmentation with DTFs.

>>>>

\documentclass[12pt,toc=bibnumbered, a4paper,twoside,DIV=11,BCOR=1cm]{scrbook}
%\documentclass[12pt,toc=bibnumbered, a4paper,twoside,DIV=calc]{scrbook}
%\documentclass[12pt,toc=bibnumbered, a4paper,twoside]{book}

\usepackage[colorlinks=True, citecolor=blue!50!black, linkcolor=red!50!black, urlcolor=blue!70!black]{hyperref}
\usepackage{refstyle}
\usepackage{amssymb}
\usepackage{amstext}
\usepackage{amsmath}
\usepackage{microtype}
\usepackage{natbib}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{tabu}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{mdwlist}
\usepackage[noend]{algpseudocode}
\usepackage[small]{caption}
\usepackage{setspace}
\usepackage{color}
\usepackage{minted}
\usepackage[german,english]{babel}
\usepackage[export]{adjustbox}

%\renewcommand*\sfdefault{avant}
\usepackage{helvet}
%\usepackage[defaultsans]{droidsans}
%\renewcommand*\sfdefault{lmssq}

@@

\newcommand\numberthis{\addtocounter{equation}{1}\tag{\theequation}}

@@

\newcommand{\given}{\, | \,}
\newcommand{\B}[1]{\mathbf{#1}}

@@

\section{Future Directions}
There are several directions for future research that we think would be
interesting to pursue as an extension of the presented results:
\paragraph{Large-Scale Weakly Supervised Object Class Segmentation}
We demonstrated a new method for object class segmentation using only weak
supervision. One of the main advantages of such a method is that it is
potentially able to exploit the large amount of weakly labeled data that
is available on the internet. Using additional, weakly labeled training data,
and evaluating on the given, manually annotated data, is therefore a promising
path for improving the presented results.
\paragraph{Inference Machines}
Recently \citet{stoyanov2011empirical} started a new trend in structured
prediction, which is sometimes called ``inference machines''. The basic
principle is simple: the process of prediction \emph{using a given inference
procedure} is viewed as a feed-forward method for prediction, and parameters of this
prediction process are optimized directly using empirical risk minimization. The work of
\citet{stoyanov2011empirical} used loopy belief propagation as their inference
algorithm and the optimization is carried out simply using gradient descent on
the non-convex but differentiable loss function.  Other recent work in this
direction includes \citet{krahenbuhlparameter}, who used mean-field inference
in a fully connected conditional random field and \citet{jancsarylearning}, who
used closed form inference in a Gaussian CRF\@.
While these algorithms show great promise, their relation to the traditional
approach of structured prediction used in this work is mostly unclear. In particular,
if exact traditional learning is possible in a model, it is uncertain how much
in accuracy and efficiency can be gained by direct empirical risk minimization.
Only limited empirical comparison is available, and we are not aware of theoretical
work in this direction, leaving much room for future investigation.
\paragraph{Non-Linear Models}
In this work, we only considered models that are linear in the input features---though
features are highly non-linear in the original input pixels. Allowing non-linear
interactions increases the representational power of a CRF, possibly leading
to more accurate prediction results.
Kernelization of structural support vector machines is straight-forward in theory, but
had only limited success in the context of CRFs for image
segmentation~\citep{lucchi2012structured}.
Two major alternatives for non-linear CRFs were proposed in the literature,
conditional neural fields~\citep{peng2009conditional} based on neural networks,
and decision tree fields~\citep{nowozin2011decision}, based on decision trees.
Conditional neural fields have only been applied to sequence classification so far,
and extending them to our setting of semantic image segmentation would be very
interesting. Decision tree fields~(DTFs) on the other hand have been applied to loopy
graphs for image processing, but not for higher-level tasks such as semantic
segmentation. If it is possible to include context in a meaningful way, it
might be possible to address even object-centric tasks such as object class
segmentation with DTFs.

### 2013-09-22 nyu/paper.tex
use past tense when discussing literature.

\section{Related Work}
The task of dense semantic annotation of 3D maps has seen an increased interest
in recent years.  Early work includes \citet{nuchter2008towards}, who combine
6D SLAM, surface annotation, and object recognition to build semantically
annotated maps. They demonstrate their approach on a mobile robot in an indoor
environment.
%
More recently \citet{sengupta2012automatic} introduced a dataset of
semantically annotated street-scenes in a closed track, captured as pairs of
stereo images. They approach the task by jointly reasoning about 3D layout and
semantics of the scenes and produce a dense labeling on image level.
\citet{senguptaurban} extend the approach to produce a volumetric
reconstruction of the scene, together with a dense semantic labeling of the
volumetric representation. Their approach to image segmentation builds on
the hierarchical CRF approach of
\citet{ladicky2009associative}, which is similar in spirit to our approach,
but uses Potts potentials together with cross-validation to adjust parameters.

Recent approaches for indoor semantic annotation of maps mostly focused on
RGB-D images, which are now easy to obtain using structured light sensors.
\citet{stuckler2012semantic}, for example, used a Random Forest model to obtain a dense
semantic labeling of images and integrated predictions over multiple views in 3D.
They evaluated their approach on table-top and simple indoors scenes.
%
\citet{silberman2011indoor} introduced the NYU Depth Dataset V1 indoor dataset,
which consisted of a large variety of densely annotated indoor scenes, captured as RGB-D images.
Their work also introduced a baseline method for semantic segmentation of RGB-D
image, which is based on a CRF over superpixels, with unary potentials given by interest point descriptors.
While pairwise potentials for the CRF were carefully
designed for the dataset, potentials were either directly set by hand or estimated using empirical
frequencies. This is in contrast to our work, which applies structured prediction techniques
to learn potentials automatically to optimize predictive performance.
%
\citet{ren2012rgb} evaluated the design of features for semantic labeling of
RGB-D data, and use a hierarchical segmentation to provide context. While they
also define a CRF on superpixels, their model is again not learned, but a
weighted Potts model, using only a probability of boundary map, and not taking
spatial layout into account at all.
%
\citet{SilbermanECCV12} extended the NYU Depth Dataset V1 to the NYU Depth Dataset V2 that we are also
using in this work.  Their focus is on inferring support relations in indoor
scenes, such as objects resting on tables or shelfs, which in turn rest on the floor.
Their approach is based on robust estimation of 3D plane hypotheses, which are then jointly
optimized with support relations and structure classes.
\citet{SilbermanECCV12} use a complex pipeline, employing significant domain knowledge.
In this work, on the other hand, we try to learn all relevant domain specific features
directly from the data, which allows us to out-perform the work of \citet{SilbermanECCV12}
with respect to structure class segmentation.

\citet{couprie-iclr-13} approach the task of semantic segmentation of structure classes
in RGB-D using the paradigm of convolutional neural networks, extending
previous work of \citet{farabet-pami-13} and \citet{schulz2012learning}.
Similar to our approach, \citet{couprie-iclr-13} combine the output of a
pixel-based, low-level learning algorithm with an independent unsupervised
segmentation step. In contrast to their work, we improve our results by not
only averaging predictions within superpixels, but also explicitly learning
interactions between neighboring superpixels, favoring a consistent
interpretation of the whole image.

\citet{stueckler2013} extends the approach of \citet{stuckler2012semantic} to
a real-time system for online learning and prediction of semantic classes. Their
use a GPU implementation of random forests, and integrate 3D scene information
in an online fashion. They evaluate their approach on the dataset of
\citet{SilbermanECCV12} with promising results.
We use the implementation of random forest provided by
\citet{stueckler2013}, but instead of integrating predictions over time, we
focus on exploiting the structure within a single frame.

>>>>

\section{Related Work}
The task of dense semantic annotation of 3D maps has seen an increased interest
in recent years.  Early work includes \citet{nuchter2008towards}, who combined
6D SLAM, surface annotation, and object recognition to build semantically
annotated maps. They demonstrate their approach on a mobile robot in an indoor
environment.
%
More recently \citet{sengupta2012automatic} introduced a dataset of
semantically annotated street-scenes in a closed track, captured as pairs of
stereo images. They approach the task by jointly reasoning about 3D layout and
semantics of the scenes and produce a dense labeling on image level.
\citet{senguptaurban} extended the approach to produce a volumetric
reconstruction of the scene, together with a dense semantic labeling of the
volumetric representation. Their approach to image segmentation builds on
the hierarchical CRF approach of
\citet{ladicky2009associative}, which is similar in spirit to our approach,
but used Potts potentials together with cross-validation to adjust parameters.

Recent approaches for indoor semantic annotation of maps mostly focused on
RGB-D images, which are now easy to obtain using structured light sensors.
\citet{stuckler2012semantic}, for example, used a Random Forest model to obtain a dense
semantic labeling of images and integrated predictions over multiple views in 3D.
They evaluated their approach on table-top and simple indoors scenes.
%
\citet{silberman2011indoor} introduced the NYU Depth Dataset V1 indoor dataset,
which consisted of a large variety of densely annotated indoor scenes, captured as RGB-D images.
Their work also introduced a baseline method for semantic segmentation of RGB-D
image, which is based on a CRF over superpixels, with unary potentials given by interest point descriptors.
While pairwise potentials for the CRF were carefully
designed for the dataset, potentials were either directly set by hand or estimated using empirical
frequencies. This is in contrast to our work, which applies structured prediction techniques
to learn potentials automatically to optimize predictive performance.
%
\citet{ren2012rgb} evaluated the design of features for semantic labeling of
RGB-D data, and use a hierarchical segmentation to provide context. While they
also define a CRF on superpixels, their model is again not learned, but a
weighted Potts model, using only a probability of boundary map, and not taking
spatial layout into account at all.
%
\citet{SilbermanECCV12} extended the NYU Depth Dataset V1 to the NYU Depth Dataset V2 that we are also
using in this work.  Their focus is on inferring support relations in indoor
scenes, such as objects resting on tables or shelfs, which in turn rest on the floor.
Their approach is based on robust estimation of 3D plane hypotheses, which are then jointly
optimized with support relations and structure classes.
\citet{SilbermanECCV12} used a complex pipeline, employing significant domain knowledge.
In this work, on the other hand, we try to learn all relevant domain specific features
directly from the data, which allows us to out-perform the work of \citet{SilbermanECCV12}
with respect to structure class segmentation.

\citet{couprie-iclr-13} approached the task of semantic segmentation of structure classes
in RGB-D using the paradigm of convolutional neural networks, extending
previous work of \citet{farabet-pami-13} and \citet{schulz2012learning}.
Similar to our approach, \citet{couprie-iclr-13} combined the output of a
pixel-based, low-level learning algorithm with an independent unsupervised
segmentation step. In contrast to their work, we improve our results by not
only averaging predictions within superpixels, but also explicitly learning
interactions between neighboring superpixels, favoring a consistent
interpretation of the whole image.

\citet{stueckler2013} extended the approach of \citet{stuckler2012semantic} to
a real-time system for online learning and prediction of semantic classes.
Their method use a GPU implementation of random forests, and integrate 3D scene
information in an online fashion. They evaluated their approach on the dataset
of \citet{SilbermanECCV12} with promising results.  We use the implementation
of random forest provided by \citet{stueckler2013}, but instead of integrating
predictions over time, we focus on exploiting the structure within a single
frame.

### 2013-09-22 partial_supervision/paper.tex
use past tense when discussing literature.

Multi-instance learning is a natural formulation for image classification and
has been successfully applied to this task~\citep{zhou2007multi}. We propose to
go a step further and apply multi-instance learning to the task of object-class
segmentation in natural images, by also classifying instances, not only bags.
In this, we follow the work of \citet{liconvex2010} and \citet{zha2008joint}, who not
only learn $f_{MI}$, but also $f_{I}$.

@@

\citet{gaertner2002multi} introduced the concept of a multi-instance
kernel on bags, defined in terms of a kernel on instances. 
The basic principle of the multi-instance kernel is similar to a soft-max over instances in
each bag. This can be viewed as approximating the kernel value of the ``closest pair'' given by two bags. \citet{gaertner2002multi} show that the multi-instance kernel
is able to separate bags if and only if the original kernel on instances is able to separate the underlying concepts.
The method of multi-instance kernels has a particular appeal in that it transforms a multi-instance problem into a standard
classification problem by using an appropriate kernel. The downside of this approach is that it does
not directly label instances, only bags.
 %and that it assumes that instances inside a bag have i.i.d.
%labels.

\citet{zhou2009multi} explicitly address the fact that instances are not
independent within a bag , leading to an algorithm that can take advantage of
possible correlations. Computational costs of their algorithm does not scale
well with the number of instances, although a heuristic algorithm is proposed
to overcome this restriction. 
%FIXME where does this sentence go?
\citet{zhou2009multi} demonstrated only a slight
advantage of their algorithm over the MI-kernel of \citet{gaertner2002multi},
so we use the MI-kernel for better scalability.

\citet{liconvex2010} compute likelihood ratios for instances, giving a new
convex formulation of the multi-instance problem. Using these likelihood
ratios, classification can be performed directly on the instances, provided an
appropriate threshold for classifying instances as positive is known. We
circumvent this problem by applying the same classifier to instances and bags,
thereby obtaining hard class decisions for each instance.

>>>>

Multi-instance learning is a natural formulation for image classification and
has been successfully applied to this task~\citep{zhou2007multi}. We propose to
go a step further and apply multi-instance learning to the task of object-class
segmentation in natural images, by also classifying instances, not only bags.
In this, we follow the work of \citet{liconvex2010} and \citet{zha2008joint}, who not
only learned $f_{MI}$, but also $f_{I}$.

@@

\citet{gaertner2002multi} introduced the concept of a multi-instance
kernel on bags, defined in terms of a kernel on instances. 
The basic principle of the multi-instance kernel is similar to a soft-max over instances in
each bag. This can be viewed as approximating the kernel value of the ``closest pair'' given by two bags. \citet{gaertner2002multi} showed that the multi-instance kernel
is able to separate bags if and only if the original kernel on instances is able to separate the underlying concepts.
The method of multi-instance kernels has a particular appeal in that it transforms a multi-instance problem into a standard
classification problem by using an appropriate kernel. The downside of this approach is that it does
not directly label instances, only bags.
 %and that it assumes that instances inside a bag have i.i.d.
%labels.

\citet{zhou2009multi} explicitly addressed the fact that instances are not
independent within a bag , leading to an algorithm that can take advantage of
possible correlations. Computational costs of their algorithm does not scale
well with the number of instances, although a heuristic algorithm is proposed
to overcome this restriction. 
%FIXME where does this sentence go?
\citet{zhou2009multi} demonstrated only a slight
advantage of their algorithm over the MI-kernel of \citet{gaertner2002multi},
so we use the MI-kernel for better scalability.

\citet{liconvex2010} computed likelihood ratios for instances, giving a new
convex formulation of the multi-instance problem. Using these likelihood
ratios, classification can be performed directly on the instances, provided an
appropriate threshold for classifying instances as positive is known. We
circumvent this problem by applying the same classifier to instances and bags,
thereby obtaining hard class decisions for each instance.

### 2013-09-22 pystruct/paper.tex
use past tense when discussing literature.

Unfortunately only few implementations for learning structured prediction are
publicly available---many applications are based on the non-free implementation
of~\citet{joachims2009cutting}.
In this section, we introduce our implementation, \pystruct, which aims at
providing a high-quality code with an easy-to-use interface, in the high-level
Python language. This allows practitioners to efficiently test a range of
models, as well as allowing researchers to compare to baseline methods much
more easily than this is possible with current implementations. \pystruct is
BSD-licensed, allowing modification and redistribution of the code, as well as
use in commercial applications.  By embracing paradigms established in the
scientific Python community and reusing the interface of the widely-used {\sc
scikit-learn} library~\citep{pedregosa2011scikit}, \pystruct can be used in
existing projects, replacing standard classifiers. The online documentation and
examples help new users understand the somewhat abstract ideas behind
structured prediction.
We base the experiments in the rest of this work on the algorithms
implemented in \pystruct. In the following, we briefly discuss implementation
and features of the \pystruct library.

>>>>

Unfortunately only few implementations for learning structured prediction are
publicly available---many applications are based on the non-free implementation
of \citet{joachims2009cutting}.
In this section, we introduce our implementation, \pystruct, which aims at
providing a high-quality code with an easy-to-use interface, in the high-level
Python language. This allows practitioners to efficiently test a range of
models, as well as allowing researchers to compare to baseline methods much
more easily than this is possible with current implementations. \pystruct is
BSD-licensed, allowing modification and redistribution of the code, as well as
use in commercial applications.  By embracing paradigms established in the
scientific Python community and reusing the interface of the widely-used {\sc
scikit-learn} library~\citep{pedregosa2011scikit}, \pystruct can be used in
existing projects, replacing standard classifiers. The online documentation and
examples help new users understand the somewhat abstract ideas behind
structured prediction.
We base the experiments in the rest of this work on the algorithms
implemented in \pystruct. In the following, we briefly discuss implementation
and features of the \pystruct library.
